paper2_resistance_mechanisms_mixtures

### 2016-10-24 inst/documents/effectiveness_exposure_difference.Rmd
tweaking figure options for paper1 & 2

plot_fit_rs(df_base_, column='f', title='base', ylim=c(0.4,0.8))

plot_fit_rs(df_ef_, column='f', title='effectiveness', ylim=c(0.4,0.8), yblank=TRUE)

plot_fit_rs(df_ex_, column='f', title='exposure', ylim=c(0.4,0.8), yblank=TRUE)

@@

@@

>>>>

plot_fit_rs(df_base_, column='f', title='base 0.5', ylim=c(0.4,0.8))

plot_fit_rs(df_ef_, column='f', title='effectivenessI1 0.8', ylim=c(0.4,0.8), yblank=TRUE)

plot_fit_rs(df_ex_, column='f', title='exposureI1 0.8', ylim=c(0.4,0.8), yblank=TRUE)

@@

#can use cowplot to size 1st plot with y axis differently

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=5, fig.show='hold', fig.align='left', fig.cap="test A.  B. C. D."}

#todo to get grid fig working.
#think about implementing in ggplot2 to make my life easier later ?
#although I'm not sure it would ?
#allow x axis labels and title to be removed
#add axis titles outside of the plot region
#remove curve legend on plots and put it somewhere else maybe on bottom
#? allow curves to be thicker

#test of rearranging figures on a grid
#eff1  0.5  0.8
#exp
#0.5    1   2
#0.8    3   4

layout(matrix(1:4,2,2, byrow = TRUE))
#effectiveness on mixture

#plot margins
oldpar <- par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#base scenario
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#exposure 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 & expos 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

par(oldpar)

### 2016-10-24 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
tweaking figure options for paper1 & 2

#Fig1 
```{r Fig1, eval=TRUE, echo=FALSE, fig.height=7.5, fig.width=5, fig.show='hold', fig.align='left'}

@@

plotlist[[1]] <- ggplot(df_to_plot, aes(x=generation, y=freq, 
                              colour=factor(dominance,labels=c("0   recessive",
                                                               "0.5 partial",
                                                               "1   dominant")))) + 
       theme_bw() +  
       #theme(legend.position = "bottom", legend.key = element_blank()) + 
       #guides(colour = guide_legend(reverse=TRUE)) +  
       labs(colour = "dominance") +
       ylab("Resistance Allele Frequency") +   
       #coord_trans(y = "log10") +    
       geom_line()

@@

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +   
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())

plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(0.7,1))

@@

# Fig2 replicating Curtis
```{r Fig2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, fig.keep='last'}

@@

  #set layout for 2 plots
  layout(t(1:2))

  #2A
  calibration <- 1011
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )
  #we submitted the LD one but should have done the Fig1
  #plotcurtis_ld( listOut$results[[1]], listOut$results[[2]], 1, 4 )
  plotcurtis_f1( listOut$results[[1]], listOut$results[[2]], 1, 2 )

  #2B
  calibration <- 1012
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )  
  plotcurtis_f2( listOut$results[[3]], listOut$results[[1]], listOut$results[[2]], 1, 2, 3 )

@@

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.6))

@@

  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1))

@@

  plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(1,1.6))

>>>>

#Fig1 
```{r Fig1, eval=TRUE, echo=FALSE, fig.height=7.5, fig.width=6, fig.show='hold'}
#, fig.align='left'}

#PLOS fig dimensions
#Maximum width 7.5 or 5.2 to fit in text column.
#Maximum height 8.75

@@

plotlist[[1]] <- ggplot(df_to_plot, aes(x=generation, y=freq, 
                              colour=factor(dominance,labels=c("0   recessive",
                                                               "0.5 partial",
                                                               "1   dominant")))) + 
       theme_bw() +  
       #theme(legend.position = "bottom", legend.key = element_blank()) + 
       #guides(colour = guide_legend(reverse=TRUE)) +  
       labs(colour = "dominance") +
       ylab("Resistance Allele Frequency") +   
       #coord_trans(y = "log10") +    
       geom_line()
       #annotate('text',label='A)',x=-10, y=1.1)

@@

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +   
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())
       #draw_plot_label('B)') +

plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(0.7,1), labels='AUTO')

#draw_figure_label('B)', pos='top.left')

@@

# Fig2 replicating Curtis
```{r Fig2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5, fig.width=6, fig.keep='last'}

@@

  #set layout for 2 plots
  layout(t(1:2))
  par(mar=c(0.4,2.9,0,0.4)) #bltr default is c(5, 4, 4, 2)

  #2A
  calibration <- 1011
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )
  #we submitted the LD one but should have done the Fig1
  #plotcurtis_ld( listOut$results[[1]], listOut$results[[2]], 1, 4 )
  plotcurtis_f1( listOut$results[[1]], listOut$results[[2]], 1, 2 )
  #side=1=bottom, 2=left, 3=top, 4=right, adj=0 left justify, lines move outwards
  mtext('A)',side=3, adj=0, line=1)

  #2B
  calibration <- 1012
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )  
  plotcurtis_f2( listOut$results[[3]], listOut$results[[1]], listOut$results[[2]], 1, 2, 3 )
  #side=1=bottom, 2=left, 3=top, 4=right, adj=0 left justify, lines move outwards
  mtext('B)',side=3, adj=0, line=1)

@@

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.6), labels='AUTO')

@@

  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1), labels='AUTO', vjust=1)

@@

  plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(1,1.6), labels='AUTO')

### 2016-10-24 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
tweaking figure options for paper1 & 2

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab="", ylabs = FALSE, main='B.', maxX = 120 )

>>>>

#base scenario
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.', maxX = 120 )

@@

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab="", ylabs = FALSE, main='B.', maxX = 120 )
